Why is it that statistical tests for residuals are not widely used? An explanation using visual inference.

### 2023-02-28 paper_comparison/paper_comparison/paper_comparison.tex
rearrange the topics

\hypertarget{caluculation-of-p-value-effect-size-and-power}{%
\section{Caluculation of p-value, effect size and
power}\label{caluculation-of-p-value-effect-size-and-power}}

Visual inference is

To be able to properly compare conventional tests to visual tests, we
need to define the effect size of the residual departure, the power of
the tests under a certain level of effect size,

\hypertarget{caluculation-of-effect-size}{%
\subsubsection{Caluculation of effect
size}\label{caluculation-of-effect-size}}

\hypertarget{caluculation-of-p-value}{%
\subsubsection{Caluculation of p-value}\label{caluculation-of-p-value}}

@@

\hypertarget{caluculation-of-power}{%
\subsubsection{Caluculation of power}\label{caluculation-of-power}}

@@

>>>>

\hypertarget{caculation-of-p-value-and-power}{%
\section{Caculation of p-value and
power}\label{caculation-of-p-value-and-power}}

\hypertarget{p-value}{%
\subsection{\texorpdfstring{\(p\)-value}{p-value}}\label{p-value}}

@@

\hypertarget{power}{%
\subsection{Power}\label{power}}

@@

\hypertarget{effect-size}{%
\subsection{Effect size}\label{effect-size}}
